---
title: "data cleaning part II"
author: "Annie George"
date: "November 21, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(readxl)
library(xlsx)
library(sqldf)
library(plyr)
library(tidyr)
library(caret)
library(janitor)
library(MASS)
library(fpp2)
```
<b>Part I. Cleaning</b>
Read the merged driver file for sun care products and clean the column names to lower case and underscore eg: week_start
```{r}
sun=read_excel("sun_drivers.xlsx",  col_names=TRUE)
sun=clean_names(sun)
```
1. Fill in UNKNOWN category with known category values for the product
2. Fill in UNKNOWN subcategory with known category values for the product
3. Fixing title with similar names but differnt caps (IDEA!!! Cluster to see the names have an effect such as ULTRA, SHEER, OIL_FREE, BROAD SPECTRUM)
```{r}
#1. Find titles with category UNKNOWN
#2. Get all unique category for the title (with UNKNOW) to provide a value for UNKNOWN 
#3. Manipulated 2 entries, 2 more UNKNOWNS remain
temp=unique(sun[sun$category == "UNKNOWN" & !is.na(sun$category),c("title", "category", "product_group")])
unique(sun[sun$title==temp$title, c("title", "category", "product_group")])
sun$category[sun$title=="Neutrogena Sunscreen Ultra Sheer Stick SPF 70, 1.5 Ounce" & sun$category=="UNKNOWN"] = "1900  Mass Skin Care - Pantry"
sun$category[sun$title=="Neutrogena, Ultra Sheer Sunblock Dry-Touch, SPF 100+, 3 fl oz" & sun$category=="UNKNOWN"] = "0900 GM/HBC"

#1. Find titles with category UNKNOWN
#2. Get all unique category for the title (with UNKNOW) to provide a value for UNKNOWN 
#3. Manipulated 2 entries, 2 more UNKNOWNS remain
temp=unique(sun[sun$subcategory == "UNKNOWN" & !is.na(sun$subcategory),c("title", "subcategory", "product_group")])
unique(sun[sun$title==temp$title, c("title", "subcategory", "product_group")])
sun$subcategory[sun$title=="Neutrogena Sunscreen Ultra Sheer Stick SPF 70, 1.5 Ounce" & sun$subcategory=="UNKNOWN"] = "1970  Sun"
sun$subcategory[sun$title=="Neutrogena, Ultra Sheer Sunblock Dry-Touch, SPF 100+, 3 fl oz" & sun$subcategory=="UNKNOWN"] = "0930 Beauty"

#Fix the title
temp=unique(sun[,c("title", "category", "subcategory", "product_group")])
unique(sun[sun$title==temp$title, c("title", "category", "subcategory", "product_group")]) 
sun$title[sun$title == "Neutrogena Ultra Sheer Dry-Touch Sunscreen Broad Spectrum SPF 45, 3 Fl. Oz,"] = "Neutrogena Ultra Sheer Dry-Touch Sunscreen, Broad Spectrum Spf 45, 3 Fl. Oz"
sun$title[sun$title == "Neutrogena Wet Skin Kids Stick Sunscreen Broad Spectrum SPF 70, 0.47 Ounce"] = "Neutrogena Wet Skin Kids Stick Sunscreen Broad Spectrum Spf 70, 0.47 Oz."
sun$title[sun$title == "Neutrogena Ultra Sheer Dry-Touch Sunscreen Broad Spectrum SPF 100, 3 Fluid"] = "Neutrogena Ultra Sheer Dry-Touch Sunscreen Broad Spectrum SPF 100, 3 Fl. Oz"
sun$title[sun$title == "Neutrogena Ultra Sheer Dry-Touch Sunscreen, Broad Spectrum Spf 100, 3 Fl. O"] = "Neutrogena Ultra Sheer Dry-Touch Sunscreen Broad Spectrum SPF 100, 3 Fl. Oz"
sun$title[sun$title == "Neutrogena Wet Skin Kids Stick Sunscreen Broad Spectrum Spf 70, 0.47 Oz."] = "Neutrogena Wet Skin Kids Stick Sunscreen Broad Spectrum SPF 70, 0.47 Oz"
sun$title[sun$title == "Neutrogena Ultra Sheer Face & Body Stick Sunscreen Broad Spectrum Spf 70, 1"] = "Neutrogena Ultra Sheer Face & Body Stick Sunscreen Broad Spectrum SPF 70, 1"
sun$title[sun$title == "Neutrogena Age Shield Face Oil-Free Lotion Sunscreen Broad Spectrum Spf 110"] = "Neutrogena Age Shield Face Oil-Free Lotion Sunscreen Broad Spectrum SPF 110"
sun$title[sun$title == "Neutrogena Wet Skin Kids Sunscreen Spray, Twin Pack, 2 Count"] = "Neutrogena Wet Skin Kids Sunscreen Spray, Twin Pack"
sun$title[sun$title == "Neutrogena SPF 70 Plus Wet Skin Kids Sunscreen Stick Broad Spectrum, 0.47 O"] = "Neutrogena SPF 70 Plus Wet Skin Kids Suncreen Stick Broad Spectrum, 0.47 Ou"
sun$title[sun$title == "Neutrogena Ultra Sheer Dry Touch Sunscreen SPF 100, 3 oz., (Packaging May V"] = "Neutrogena Ultra Sheer SPF 100 Dry Touch Sunscreen, 3 ounce"
sun$title[sun$title ==  "Neutrogena Beach Defense Sunscreen Body Lotion Broad Spectrum Spf 70, 6.7 O"] = "Neutrogena Beach Defense Sunscreen Lotion Broad Spectrum SPF 70, 6.7 Oz" 

sun$title[sun$title ==  "Neutrogena Ultra Sheer Dry-Touch Sunscreen Broad Spectrum SPF 100, 3 Fl. Oz"]=  "Neutrogena Ultra Sheer Dry-Touch Sunscreen Broad Spectrum SPF 100, 3 fl. oz" 
sun$title[sun$title ==  "Neutrogena Age Shld Ss Spf-110 3 OZ"] =  "NEUTROGENA AGE SHLD SS SPF-110 3 OZ" 
sun$title[sun$title ==   "Neutrogena Ultra Sheer Drytouch Sunscreen, SPF 45, 3 Ounce Twin pack"]=  "Neutrogena Ultra Sheer Drytouch Sunscreen, SPF 45, 3 Ounce (Pack of 2)" 
sun$title[sun$title ==    "Neutrogena Ultra Sheer SPF 100 Dry Touch Sunscreen, 3 ounce"]=  "Neutrogena Ultra Sheer SPF 100 Dry Touch Sunscreen, 3 Ounce"   
sun$title[sun$title ==     "Neutrogena Age Shield Face Oil-Free Lotion Sunscreen Broad Spectrum SPF 110"]=  "Neutrogena Age Shield Face Lotion Sunscreen Broad Spectrum SPF 110, 3.0 fl."  

unique(sun$title)
```

Add week number 1-52
```{r}
library(epitools)
sun$week_number=as.factor(as.week(sun$week_start, format = "%y-%m-%d", sunday= TRUE)$week)
```

Converting categorical to factors for modeling
```{r}
sun$average_customer_reviews_int = as.factor(round(sun$average_customer_review))
sun$title=as.factor(sun$title)
sun$asin=as.factor(sun$asin)
sun$upc_code=as.factor(sun$upc_code)
sun$product_group=as.factor(sun$product_group)
sun$category=as.factor(sun$category)
sun$subcategory=as.factor(sun$subcategory)
sun$replenishment_category=as.factor(sun$replenishment_category)
sun$platform1 = as.factor(sun$platform1)
sun$platform2 = as.factor(sun$platform2)
```

1. Find the NAs for rank fields and average ordered 
2. Remove extra NAs
Fix all those with ranks
```{r}
sum(is.na(sun))
colSums(is.na(sun))

#Remove NA rows for week start
sun=sun[!is.na(sun$week_start),]

#All average ordered/shipped price with NAs have ordered/shipped amount as 0, hence the NA's will be set as zeros
sun[is.na(sun$average_ordered_price),c("average_ordered_price", "ordered_amount")]
sun$average_ordered_price[is.na(sun$average_ordered_price)] = 0 

sun[is.na(sun$average_shipped_price),c("average_shipped_price", "shipped_amount")]
sun$average_shipped_price[is.na(sun$average_shipped_price)] = 0


#Set NAs in cat/subcat ordered sales rank based on ordered amount, If ordered amount is zero, set it as zero
#Set NAs in cat/subcat ordered units rank based on ordered units, If ordered units is zero, set it as zero
#Set NAs in cat/subcat shipped sales rank based on shipped amount, If shipped amount is zero, set it as zero
#Set NAs in cat/subcat shipped units rank based on shipped units, If shipped units is zero, set it as zero
colSums(is.na(sun))
sun[is.na(sun$amazon_category_ordered_sales_rank & sun$ordered_amount == 0),c("amazon_category_ordered_sales_rank", "amazon_category_ordered_sales_rank", "amazon_subcategory_ordered_sales_rank", "ordered_amount")]
sun$amazon_category_ordered_sales_rank[is.na(sun$amazon_category_ordered_sales_rank) & sun$ordered_amount == 0] = 0

sun$amazon_subcategory_ordered_sales_rank[is.na(sun$amazon_subcategory_ordered_sales_rank) & sun$ordered_amount == 0] = 0

sun$amazon_ordered_sales_rank[is.na(sun$amazon_ordered_sales_rank) & sun$ordered_amount == 0] = 0

sun$amazon_shipped_sales_rank[is.na(sun$amazon_shipped_sales_rank) & sun$shipped_amount == 0] = 0

sun$amazon_category_shipped_sales_rank[is.na(sun$amazon_category_shipped_sales_rank) & sun$shipped_amount == 0] = 0

sun$amazon_subcategory_shipped_sales_rank[is.na(sun$amazon_subcategory_shipped_sales_rank) & sun$shipped_amount == 0] = 0

sun$amazon_category_ordered_units_rank[is.na(sun$amazon_category_ordered_units_rank) & sun$ordered_units == 0] = 0

sun$amazon_subcategory_ordered_units_rank[is.na(sun$amazon_subcategory_ordered_units_rank) & sun$ordered_units == 0] = 0

sun$amazon_ordered_units_rank[is.na(sun$amazon_ordered_units_rank) & sun$ordered_units == 0] = 0

sun$amazon_category_shipped_units_rank[is.na(sun$amazon_category_shipped_units_rank) & sun$shipped_units == 0] = 0

sun$amazon_subcategory_shipped_units_rank[is.na(sun$amazon_subcategory_shipped_units_rank) & sun$shipped_units == 0] = 0

sun$amazon_shipped_units_rank[is.na(sun$amazon_shipped_units_rank) & sun$shipped_units == 0] = 0

#Page view ranks with NA and having zero ordered units will be set as zero
colSums(is.na(sun))
sun[is.na(sun$page_views_rank),c("amazon_category_ordered_sales_rank", "amazon_category_ordered_sales_rank", "amazon_subcategory_ordered_sales_rank", "ordered_units", "page_views_rank")]
sun$page_views_rank[is.na(sun$page_views_rank) & sun$ordered_units == 0] = 0

#That still leaves us with 23 rows with field ranks as NA. Hence these will be removed from analysis 
colSums(is.na(sun))
sun[is.na(sun$page_views_rank),]
sun=sun[!is.na(sun$page_views_rank),] 

colSums(is.na(sun))
sun=sun[!is.na(sun$amazon_ordered_sales_rank),] 
```

Set a new variable which will say if the product is sold only in prime or online or both
only prime = pn, only com =com, both =pncom
```{r}
sun[is.na(sun$platform1), c("platform1", "platform2")]
sun$platform_type="NA"
sun$platform_type[!is.na(sun$platform1) & !is.na(sun$platform2)] = "pncom" 
sun$platform_type[(is.na(sun$platform1) & sun$platform2 == "com") | (is.na(sun$platform2) & sun$platform1 == "com")] = "com"
sun$platform_type[(is.na(sun$platform1) & sun$platform2 == "pn") | (is.na(sun$platform2) & sun$platform1 == "pn")] = "pn" 
sun$platform_type
```

Tweak box cox lambda order
```{r}
sun_ts=read_excel("sun_care_ts.xlsx",  col_names=TRUE)
names(sun_ts)
sun_ts=clean_names(sun_ts)
sun$week_start = as.Date(sun$week_start)
sun_ts$week_of_week_start = as.Date(sun_ts$week_of_week_start)
names(sun_ts)
library(sqldf)
library(dplyr)
library(chron)
library(timeDate)
library(lubridate)
holiday=sqldf('select b.national_holiday
      from sun a
       join  sun_ts b
      on a.week_start =b.week_of_week_start ')
sun=cbind(sun, "holiday"=holiday)
sun=sun[!sun$week_start == "2017-05-21",]

write.xlsx(sun, "clean_data.xlsx")
```
Data exploration
```{r}
ggplot(sun, aes(x=shipped_units)) + geom_histogram(fill="blue")
#outlier for just one product
sun[sun$shipped_units > 6000,] 
sun[sun$title=="Neutrogena Ultra Sheer Dry-Touch Sunscreen Broad Spectrum SPF 100, 3 Fl. Oz",]

ggplot(sun[sun$title=="Neutrogena Ultra Sheer Dry-Touch Sunscreen Broad Spectrum SPF 100, 3 Fl. Oz",], aes(y=shipped_units, x=week_start)) +
  geom_line() + ggtitle("Shipped units for Neutrogena Ultra Sheer Dry-Touch Sunscreen Broad Spectrum SPF 100, 3 Fl. Oz")


ggplot(sun, aes(x=shipped_units, y=orders)) + geom_line(col="blue")
ggplot(sun, aes(x=amazon_ordered_sales_rank)) + geom_histogram(fill="blue")
ggplot(sun, aes(x=amazon_ordered_sales_rank, y=shipped_units)) + geom_line(col="blue")
ggplot(sun, aes(x=amazon_category_ordered_sales_rank, y=shipped_units)) + geom_line(col="blue")
ggplot(sun, aes(x=amazon_subcategory_ordered_sales_rank, y=shipped_units)) + geom_line(col="blue")
ggplot(sun, aes(x=amazon_category_ordered_units_rank, y=shipped_units)) + geom_line(col="blue")
ggplot(sun, aes(x=amazon_subcategory_ordered_units_rank, y=shipped_units)) + geom_line(col="blue")
ggplot(sun, aes(x=amazon_subcategory_shipped_units_rank, y=shipped_units)) + geom_line(col="blue")
ggplot(sun, aes(x=amazon_subcategory_shipped_sales_rank, y=shipped_units)) + geom_line(col="blue")
ggplot(sun, aes(x=title, y=shipped_units)) + geom_bar(col="blue")

```

