---
title: "data cleaning"
author: "Annie George"
date: "November 6, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(readxl)
library(xlsx)
library(sqldf)
library(plyr)
library(tidyr)
library(caret)
library(janitor)
```

```{r}
#read monthly shipment/pos
sun=read_excel("sun_drivers.xlsx",  col_names=TRUE)
sun=clean_names(sun)
dates=sun[,c(2,3,8)]

```

```{r}
#sun[is.na(sun)]=0

#convert avg customer review to integer
sun$average_customer_reviews_int = as.factor(round(sun$average_customer_review))
sun$title=as.factor(sun$title)
sun$asin=as.factor(sun$asin)
sun$upc_code=as.factor(sun$upc_code)
sun$product_group=as.factor(sun$product_group)
sun$category=as.factor(sun$category)
sun$subcategory=as.factor(sun$subcategory)
sun$replenishment_category=as.factor(sun$replenishment_category)
sun$platform1 = as.factor(sun$platform1)
sun$platform2 = as.factor(sun$platform2)
#sun$currency_code = as.factor(sun$currency_code)
```

```{r}
sun=sun[,!names(sun) %in% c("ordered_amount_trend", "ordered_amount_year_over_year_trend", "amazon_ordered_sales_rank", "orders_trend", "orders_year_over_year_trend", "ordered_units_trend", "ordered_units_year_over_year_trend", "shipped_amount_trend", "shipped_amount_year_over_year_trend", "shipped_units_trend", "shipped_units_year_over_year_trend", "amazon_shipped_units_rank", "amazon_category_shipped_units_rank", "amazon_subcategory_shipped_units_rank ", "unfilled_customer_ordered_units_trend", "unfilled_customer_ordered_units_year_over_year_trend", "unique_visitors_trend ", "unique_visitors_year_over_year_trend", "conversion_rate_trend", "conversion_rate_year_over_year_trend",          "conversion_percentile", "x1_week_forecast", "x4_week_forecast", "x12_week_forecast", "sellable_on_hand_cost", "unsellable_on_hand_cost", "shipped_cost_of_goods_sold_trend", "shipped_cost_of_goods_sold", "shipped_cost_of_goods_sold_year_over_year_trend", "currency_code", "page_views_year_over_year_trend", "unique_visitors_trend", "page_views_trend")]

sum(is.na(sun))
colSums(is.na(sun))

sun=sun[!is.na(sun$week_start),]
#cases=sun[!complete.cases(sun),]

sun$average_ordered_price[is.na(sun$average_ordered_price) & !is.na(sun$average_shipped_price)] = sun$average_shipped_price[is.na(sun$average_ordered_price) & !is.na(sun$average_shipped_price)] 


sun$average_shipped_price[is.na(sun$average_shipped_price) & !is.na(sun$average_ordered_price)] = sun$average_ordered_price[is.na(sun$average_shipped_price) & !is.na(sun$average_ordered_price)] 

sun$average_shipped_price[is.na(sun$average_shipped_price) & !is.na(sun$list_price)] = sun$list_price[is.na(sun$average_shipped_price) & !is.na(sun$list_price)]

sun$average_ordered_price[is.na(sun$average_ordered_price) & !is.na(sun$list_price)] = sun$list_price[is.na(sun$average_ordered_price) & !is.na(sun$list_price)]

sun$amazon_category_ordered_sales_rank[is.na(sun$amazon_category_ordered_sales_rank) & sun$ordered_amount == 0] = 0
sun$amazon_subcategory_ordered_sales_rank[is.na(sun$amazon_subcategory_ordered_sales_rank) & sun$ordered_amount == 0] = 0
sun$amazon_category_ordered_units_rank[is.na(sun$amazon_category_ordered_units_rank) & sun$ordered_units == 0] = 0
sun$amazon_subcategory_ordered_units_rank[is.na(sun$amazon_subcategory_ordered_units_rank) & sun$ordered_units == 0] = 0
sun$amazon_ordered_units_rank[is.na(sun$amazon_ordered_units_rank) & sun$ordered_units == 0] = 0
sun$amazon_shipped_sales_rank[is.na(sun$amazon_shipped_sales_rank) & sun$shipped_amount == 0] = 0
sun$amazon_category_shipped_sales_rank[is.na(sun$amazon_category_shipped_sales_rank) & sun$shipped_amount == 0] = 0
sun$amazon_subcategory_shipped_sales_rank[is.na(sun$amazon_subcategory_shipped_sales_rank) & sun$shipped_amount == 0] = 0
sun$amazon_subcategory_shipped_units_rank[is.na(sun$amazon_subcategory_shipped_units_rank) & sun$shipped_units == 0] = 0


num_var = which(sapply(sun, is.numeric)) #index vector numeric variables
num_var= names(num_var) #saving names vector for use later on

factcols = c("amazon_category_ordered_sales_rank", "amazon_subcategory_ordered_sales_rank", "amazon_ordered_units_rank", "amazon_category_ordered_units_rank", "amazon_subcategory_ordered_units_rank", "amazon_shipped_sales_rank", "amazon_category_shipped_sales_rank", "amazon_subcategory_shipped_sales_rank", "amazon_subcategory_shipped_units_rank", "page_views_rank", "page_views_index", "unique_visitors_index")

sun[factcols] = lapply(sun[factcols], factor)
sapply(sun, function(x) sum(is.na(x)))
```

```{r}
sun=sun[!is.na(sun$amazon_subcategory_ordered_sales_rank), ]
sun=sun[!is.na(sun$amazon_category_ordered_units_rank), ]
sun=sun[!is.na(sun$page_views_rank), ]

sapply(sun, function(x) sum(is.na(x)))
```


#check number of numerical variables and their correlation with ordered units
```{r}
num_var = which(sapply(sun, is.numeric)) #index vector numeric variables
num_var= names(num_var) #saving names vector for use later on
cat('There are', length(num_var), 'numeric variables')
num_var

cor_numVar = cor(sun[, num_var], use="pairwise.complete.obs") #correlations of all numeric variables

#sort on decreasing correlations with ordered)units
cor_sorted = as.matrix(sort(cor_numVar[,'ordered_units'], decreasing = TRUE))
#select only high corelations
CorHigh = names(which(apply(cor_sorted, 1, function(x) abs(x)>0.5)))
cor_numVar_high = cor_numVar[CorHigh, CorHigh]

corrplot.mixed(cor_numVar_high, tl.col="black", tl.pos = "lt")

CorLow = names(which(apply(cor_sorted, 1, function(x) abs(x)<=0.5)))
cor_numVar_low = cor_numVar[CorLow, CorLow]

corrplot(cor_numVar_low, tl.col="black", tl.pos = "lt")

```

```{r}
library(epitools)
sun$week_number=as.factor(as.week(sun$week_start, format = "%y-%m-%d", sunday= TRUE)$week)
write.xlsx(sun, "sales_drivers_fields.xlsx")

```


```{r}

cat('There are', length(unique(sun$page_views_rank)), 'unique page view ranks. ')
cat('There are', length(unique(sun$amazon_category_ordered_units_rank)), 'unique amazon category ordered units rank. ')
cat('There are', length(unique(sun$amazon_subcategory_ordered_units_rank)), 'unique amazon subcategory ordered units rank. ')

cat_var = which(sapply(sun, is.factor)) #index vector numeric variables
cat_var= names(cat_var) #saving names vector for use later on
cat('There are', length(cat_var), 'categorical variables. ')
cat(' ')

cat('There are', length(unique(sun$asin)), 'unique asin. ')
cat('There are', length(unique(sun$upc_code)), 'unique upc code. ')
cat('There are', length(unique(sun$title)), 'unique sun products. ')
```
```{r}
#Insights
ggplot(sun, aes(y=amazon_category_ordered_units_rank, x=category)) + geom_boxplot()

ggplot(sun, aes(y=amazon_category_ordered_units_rank, x=product_group)) + geom_boxplot() #large variance in units ordered in beauty but more consistent in pantry  department

table(sun$category, sun$product_group)
table(sun$subcategory, sun$product_group)
table(sun$replenishment_category, sun$product_group)
#table(sun$title, sun$replenishment_category)
#table(sun$title, sun$subcategory)


```
```{r}
ggplot(sun, aes(y=ordered_units, x=category)) + geom_boxplot()  # there is more units ordered when listed under beauty product group

ggplot(sun, aes(y=ordered_units, x=product_group)) + geom_boxplot()

ggplot(sun, aes(y=average_ordered_price, x=product_group)) + geom_boxplot()

ggplot(sun, aes(x=average_ordered_price, y=ordered_units)) + geom_point()

ggplot(sun, aes(y=average_ordered_price, x=replenishment_category)) + geom_boxplot()
#ggplot(sun, aes(y=unsellable_on_hand_units, x=product_group)) + geom_boxplot()
ggplot(sun, aes(x=average_shipped_price, y=ordered_units)) + geom_point()

ggplot(sun, aes(x=amazon_category_ordered_units_rank, y=ordered_units)) + geom_point()
```






THE END

#Based on the correlation plot, average shipped price has some correlation with orderd units. The other fields whether dependent or not on ordered units is not relevant to the business problem.
```{r}
library(corrplot)

#sun[is.na(sun[-c("week_start", "week_end", "release_date")])]=0
num_var = which(sapply(sun, is.numeric)) #index vector numeric variables
num_var= names(num_var) #saving names vector for use later on

#sun[,num_var][is.na(sun[, num_var])]= 0
ship=names(sun[,(grep("ship", names(sun)))])

cor_ship=cor(sun$ordered_units, sun[,ship])

corrplot(cor_ship, tl.col="black", tl.pos = "lt")
ship1=cbind(sun[,ship[1]])
```
```{r}
sun_new=sun
sun_new=sun[,!names(sun) %in% c(ship)]
sun_new = cbind(sun_new, ship1)
```

#analyze all ranks in the dataset
Since these are ranks they need to be anlayzed more and hence only the ranks related to orders will be considered along with page view rank
```{r}
rank=names(sun[,(grep("rank", names(sun)))])
cor_rank=cor(sun$ordered_units, sun[,rank])
corrplot(cor_rank, tl.col="black", tl.pos = "lt")
rank1=sun[,rank[c(4, 5, 6, 13)]]
sun_new=sun_new[,!names(sun_new) %in% c(rank)]
sun_new = cbind(sun_new, rank1)
```

#Analyze all trends in the dataset
orders_year_over_year_trend
```{r}
trend=names(sun[,(grep("trend", names(sun)))])
cor_trend=cor(sun$ordered_units, sun[,trend])
corrplot(cor_trend, tl.col="black", tl.pos = "lt")
sun_new=sun_new[,!names(sun_new) %in% c(trend)]
```

#Analyse all indexes in the dataset
page view and unique view are highly correlated with ordered units and henec will be used for analysis 
```{r}
index=names(sun[,(grep("index", names(sun)))])
cor_index=cor(sun$ordered_units, sun[,index])
corrplot(cor_index, tl.col="black", tl.pos = "lt")

```
Assuming all sellable and unsellable units are required for analysis
```{r}
sellable=names(sun[,(grep("sellable", names(sun)))])
cor_sellable=cor(sun$ordered_units, sun[,sellable])
corrplot(cor_sellable, tl.col="black", tl.pos = "lt")
sellable1=sun[,sellable[c(1:2)]]
sun_new=sun_new[,!names(sun_new) %in% c(sellable)]
sun_new = cbind(sun_new, sellable1)
```
Analyze conversion rates
conversion not required
```{r}
conversion=names(sun[,(grep("conversion", names(sun)))])
cor_conversion=cor(sun$ordered_units, sun[,conversion])
corrplot(cor_conversion, tl.col="black", tl.pos = "lt")
sun_new=sun_new[,!names(sun_new) %in% c(conversion)]

```


Remove forecast for further analysis
```{r}
forecast=names(sun[,(grep("forecast", names(sun)))])
sun_new=sun_new[,!names(sun_new) %in% c(forecast)]
```

