---
title: "driver_modelling"
author: "Annie George"
date: "November 6, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r}
library(readxl)
library(xlsx)
library(sqldf)
library(plyr)
library(tidyr)
library(caret)
library(janitor)
library(MASS)
library(car)
```
<b>Part I. Cleaning</b>
Read the merged driver file for sun care products and clean the column names to lower case and underscore eg: week_start
```{r}
sun=read_excel("sun_drivers.xlsx",  col_names=TRUE)
sun=clean_names(sun)
```
1. Fill in UNKNOWN category with known category values for the product
2. Fill in UNKNOWN subcategory with known category values for the product
3. Fixing title with similar names but differnt caps (IDEA!!! Cluster to see the names have an effect such as ULTRA, SHEER, OIL_FREE, BROAD SPECTRUM)
```{r}
#1. Find titles with category UNKNOWN
#2. Get all unique category for the title (with UNKNOW) to provide a value for UNKNOWN 
#3. Manipulated 2 entries, 2 more UNKNOWNS remain
temp=unique(sun[sun$category == "UNKNOWN" & !is.na(sun$category),c("title", "category", "product_group")])
unique(sun[sun$title==temp$title, c("title", "category", "product_group")])
sun$category[sun$title=="Neutrogena Sunscreen Ultra Sheer Stick SPF 70, 1.5 Ounce" & sun$category=="UNKNOWN"] = "1900  Mass Skin Care - Pantry"
sun$category[sun$title=="Neutrogena, Ultra Sheer Sunblock Dry-Touch, SPF 100+, 3 fl oz" & sun$category=="UNKNOWN"] = "0900 GM/HBC"

#1. Find titles with category UNKNOWN
#2. Get all unique category for the title (with UNKNOW) to provide a value for UNKNOWN 
#3. Manipulated 2 entries, 2 more UNKNOWNS remain
temp=unique(sun[sun$subcategory == "UNKNOWN" & !is.na(sun$subcategory),c("title", "subcategory", "product_group")])
unique(sun[sun$title==temp$title, c("title", "subcategory", "product_group")])
sun$subcategory[sun$title=="Neutrogena Sunscreen Ultra Sheer Stick SPF 70, 1.5 Ounce" & sun$subcategory=="UNKNOWN"] = "1970  Sun"
sun$subcategory[sun$title=="Neutrogena, Ultra Sheer Sunblock Dry-Touch, SPF 100+, 3 fl oz" & sun$subcategory=="UNKNOWN"] = "0930 Beauty"

#Fix the title
temp=unique(sun[,c("title", "category", "subcategory", "product_group")])
unique(sun[sun$title==temp$title, c("title", "category", "subcategory", "product_group")]) 
sun$title[sun$title == "Neutrogena Ultra Sheer Dry-Touch Sunscreen Broad Spectrum SPF 45, 3 Fl. Oz,"] = "Neutrogena Ultra Sheer Dry-Touch Sunscreen, Broad Spectrum Spf 45, 3 Fl. Oz"
sun$title[sun$title == "Neutrogena Wet Skin Kids Stick Sunscreen Broad Spectrum SPF 70, 0.47 Ounce"] = "Neutrogena Wet Skin Kids Stick Sunscreen Broad Spectrum Spf 70, 0.47 Oz."
sun$title[sun$title == "Neutrogena Ultra Sheer Dry-Touch Sunscreen Broad Spectrum SPF 100, 3 Fluid"] = "Neutrogena Ultra Sheer Dry-Touch Sunscreen Broad Spectrum SPF 100, 3 Fl. Oz"
sun$title[sun$title == "Neutrogena Ultra Sheer Dry-Touch Sunscreen Broad Spectrum SPF 100, 3 Fl. oz"] = "Neutrogena Ultra Sheer Dry-Touch Sunscreen Broad Spectrum SPF 100, 3 Fl. Oz"

sun$title[sun$title == "Neutrogena Ultra Sheer Dry-Touch Sunscreen, Broad Spectrum Spf 100, 3 Fl. O"] = "Neutrogena Ultra Sheer Dry-Touch Sunscreen Broad Spectrum SPF 100, 3 Fl. Oz"
sun$title[sun$title == "Neutrogena Wet Skin Kids Stick Sunscreen Broad Spectrum Spf 70, 0.47 Oz."] = "Neutrogena Wet Skin Kids Stick Sunscreen Broad Spectrum SPF 70, 0.47 Oz"
sun$title[sun$title == "Neutrogena Ultra Sheer Face & Body Stick Sunscreen Broad Spectrum Spf 70, 1"] = "Neutrogena Ultra Sheer Face & Body Stick Sunscreen Broad Spectrum SPF 70, 1"
sun$title[sun$title == "Neutrogena Age Shield Face Oil-Free Lotion Sunscreen Broad Spectrum Spf 110"] = "Neutrogena Age Shield Face Oil-Free Lotion Sunscreen Broad Spectrum SPF 110"
sun$title[sun$title == "Neutrogena Wet Skin Kids Sunscreen Spray, Twin Pack, 2 Count"] = "Neutrogena Wet Skin Kids Sunscreen Spray, Twin Pack"
sun$title[sun$title == "Neutrogena SPF 70 Plus Wet Skin Kids Sunscreen Stick Broad Spectrum, 0.47 O"] = "Neutrogena SPF 70 Plus Wet Skin Kids Suncreen Stick Broad Spectrum, 0.47 Ou"
sun$title[sun$title == "NEUTROGENA AGE SHLD SS SPF-110 3 OZ"] = "Neutrogena Age Shld Ss Spf-110 3 OZ" 
sun$title[sun$title == "Neutrogena Ultra Sheer Drytouch Sunscreen, SPF 45, 3 Ounce (Pack of 2)"] = "Neutrogena Ultra Sheer Drytouch Sunscreen, SPF 45, 3 Ounce Twin pack" 

sun$title[sun$title == "Neutrogena Ultra Sheer Dry Touch Sunscreen SPF 100, 3 oz., (Packaging May V"] = "Neutrogena Ultra Sheer Dry-Touch Sunscreen Broad Spectrum SPF 100, 3 Fl. Oz" 

sun$title[sun$title == "Neutrogena, Age Shield Sunblock Lotion Face, SPF 110, 3 fl oz"] = "Neutrogena, Age Shield Sunblock Lotion Face, SPF 110, 3 fl oz"


sun$title[sun$title == "Neutrogena Beach Defense Sunscreen Body Lotion Broad Spectrum Spf 70, 6.7 O"] = "Neutrogena Beach Defense Sunscreen Lotion Broad Spectrum SPF 70, 6.7 Oz"

sun$title[sun$title == "Neutrogena Beach Defense Sunscreen Lotion with Broad Spectrum SPF 70 Protec"] = "Neutrogena Beach Defense Sunscreen Lotion Broad Spectrum SPF 70, 6.7 Oz"

unique(sun[,c("category", "release_date")])
unique(sun[sun$title==temp$title, c("title", "category", "subcategory", "product_group", "release_date")]) 
```

Add week number 1-52
```{r}
library(epitools)
sun$week_number=as.factor(as.week(sun$week_start, format = "%y-%m-%d", sunday= TRUE)$week)
```

Converting categorical to factors for modeling
```{r}
sun$average_customer_reviews_int = as.factor(round(sun$average_customer_review))
sun$title=as.factor(sun$title)
sun$asin=as.factor(sun$asin)
sun$upc_code=as.factor(sun$upc_code)
sun$product_group=as.factor(sun$product_group)
sun$category=as.factor(sun$category)
sun$subcategory=as.factor(sun$subcategory)
sun$replenishment_category=as.factor(sun$replenishment_category)
sun$platform1 = as.factor(sun$platform1)
sun$platform2 = as.factor(sun$platform2)
```

1. Find the NAs for rank fields and average ordered 
2. Remove extra NAs
3. Fix all those with ranks
```{r}
sum(is.na(sun))
colSums(is.na(sun))

#Remove NA rows for week start
sun=sun[!is.na(sun$week_start),]

#All average ordered/shipped price with NAs have ordered/shipped amount as 0, hence the NA's will be set as zeros
sun[is.na(sun$average_ordered_price),c("average_ordered_price", "ordered_amount")]
sun$average_ordered_price[is.na(sun$average_ordered_price)] = 0 

sun[is.na(sun$average_shipped_price),c("average_shipped_price", "shipped_amount")]
sun$average_shipped_price[is.na(sun$average_shipped_price)] = 0


#Set NAs in cat/subcat ordered sales rank based on ordered amount, If ordered amount is zero, set it as zero
#Set NAs in cat/subcat ordered units rank based on ordered units, If ordered units is zero, set it as zero
#Set NAs in cat/subcat shipped sales rank based on shipped amount, If shipped amount is zero, set it as zero
#Set NAs in cat/subcat shipped units rank based on shipped units, If shipped units is zero, set it as zero
colSums(is.na(sun))
sun[is.na(sun$amazon_category_ordered_sales_rank & sun$ordered_amount == 0),c("amazon_category_ordered_sales_rank", "amazon_category_ordered_sales_rank", "amazon_subcategory_ordered_sales_rank", "ordered_amount")]
sun$amazon_category_ordered_sales_rank[is.na(sun$amazon_category_ordered_sales_rank) & sun$ordered_amount == 0] = 0

sun$amazon_subcategory_ordered_sales_rank[is.na(sun$amazon_subcategory_ordered_sales_rank) & sun$ordered_amount == 0] = 0

sun$amazon_ordered_sales_rank[is.na(sun$amazon_ordered_sales_rank) & sun$ordered_amount == 0] = 0

sun$amazon_shipped_sales_rank[is.na(sun$amazon_shipped_sales_rank) & sun$shipped_amount == 0] = 0

sun$amazon_category_shipped_sales_rank[is.na(sun$amazon_category_shipped_sales_rank) & sun$shipped_amount == 0] = 0

sun$amazon_subcategory_shipped_sales_rank[is.na(sun$amazon_subcategory_shipped_sales_rank) & sun$shipped_amount == 0] = 0

sun$amazon_category_ordered_units_rank[is.na(sun$amazon_category_ordered_units_rank) & sun$ordered_units == 0] = 0

sun$amazon_subcategory_ordered_units_rank[is.na(sun$amazon_subcategory_ordered_units_rank) & sun$ordered_units == 0] = 0

sun$amazon_ordered_units_rank[is.na(sun$amazon_ordered_units_rank) & sun$ordered_units == 0] = 0

sun$amazon_category_shipped_units_rank[is.na(sun$amazon_category_shipped_units_rank) & sun$shipped_units == 0] = 0

sun$amazon_subcategory_shipped_units_rank[is.na(sun$amazon_subcategory_shipped_units_rank) & sun$shipped_units == 0] = 0

sun$amazon_shipped_units_rank[is.na(sun$amazon_shipped_units_rank) & sun$shipped_units == 0] = 0

#Page view ranks with NA and having zero ordered units will be set as zero
colSums(is.na(sun))
sun[is.na(sun$page_views_rank),c("amazon_category_ordered_sales_rank", "amazon_category_ordered_sales_rank", "amazon_subcategory_ordered_sales_rank", "ordered_units", "page_views_rank")]
sun$page_views_rank[is.na(sun$page_views_rank) & sun$ordered_units == 0] = 0

#That still leaves us with 23 rows with field ranks as NA. Hence these will be removed from analysis 
colSums(is.na(sun))
sun[is.na(sun$page_views_rank),]
sun=sun[!is.na(sun$page_views_rank),] 

colSums(is.na(sun))
sun=sun[!is.na(sun$amazon_ordered_sales_rank),] 
```

Set a new variable which will say if the product is sold only in prime or online or both
only prime = pn, only com =com, both =pncom
```{r}
sun[is.na(sun$platform1), c("platform1", "platform2")]
sun$platform_type="NA"
sun$platform_type[!is.na(sun$platform1) & !is.na(sun$platform2)] = "pncom" 
sun$platform_type[(is.na(sun$platform1) & sun$platform2 == "com") | (is.na(sun$platform2) & sun$platform1 == "com")] = "com"
sun$platform_type[(is.na(sun$platform1) & sun$platform2 == "pn") | (is.na(sun$platform2) & sun$platform1 == "pn")] = "pn" 
```
Analysis before finalizing the file

```{r}
#avg_list=sun %>%group_by(title) %>%summarise("avg_price" = mean(list_price))
#ggplot(avg_list, aes(y=sort(avg_price), x=title)) + geom_bar(stat="identity") +coord_flip()
#avg_list_upc=sun %>% select(upc_code, list_price) %>%group_by(upc_code) %>%summarise(avg_price=mean(list_price)) 
#ggplot(avg_list_upc, aes(y=(avg_price), x=upc_code)) + geom_bar(stat="identity") +coord_flip()
unique(sun[sun$list_price==0,c("title", "upc_code", "list_price", "ordered_units", "shipped_units")])
table("category"=sun$category, "subcategory"=sun$subcategory)
unique(sun[sun$category=="UNKNOWN", c("title", "category")])
(sun[sun$title=="Neutrogena Age Shld Ss Spf-110 3 OZ", c("title","shipped_units", "ordered_units")])

#can remove the product as it has no sales by any means - NO
sun=sun[!sun$title=="Neutrogena Age Shld Ss Spf-110 3 OZ", ]

unique(sun[, c("title", "category", "subcategory", "asin", "upc_code")]) %>% group_by(category, subcategory) 

unique(sun[sun$list_price==0, c("category", "subcategory", "title", "ordered_units", "shipped_units")])
```
Tweak box cox lambda order
```{r}
sun$diff_units=sun$ordered_units -  sun$shipped_units
hist(BoxCox(sun$ordered_units, lambda=0.4))
sun$transformed_order_units=BoxCox(sun$ordered_units, lambda=0.4)
write.xlsx(sun, "clean_data.xlsx")
```

Remove all trends, forecasts, currency code, shipped cost of goods sold
Check collinearity


```{r}
sun=read_excel("clean_data.xlsx",  col_names=TRUE)
sun$average_customer_reviews_int = as.factor(round(sun$average_customer_review))
sun$title=as.factor(sun$title)
sun$asin=as.factor(sun$asin)
sun$upc_code=as.factor(sun$upc_code)
sun$product_group=as.factor(sun$product_group)
sun$category=as.factor(sun$category)
sun$subcategory=as.factor(sun$subcategory)
sun$replenishment_category=as.factor(sun$replenishment_category)
sun$platform1 = as.factor(sun$platform1)
sun$platform2 = as.factor(sun$platform2)
sun$platform_type = as.factor(sun$platform_type)

sun=sun[,!names(sun) %in% c("ordered_amount_trend", 
                            "ordered_amount_year_over_year_trend", 
                            "orders_trend", "orders_year_over_year_trend", 
                            "ordered_units_trend", 
                            "ordered_units_year_over_year_trend", 
                            "shipped_amount_trend", 
                            "shipped_amount_year_over_year_trend", 
                            "shipped_units_trend", 
                            "shipped_units_year_over_year_trend",  
                            "unfilled_customer_ordered_units_trend", 
                            "unfilled_customer_ordered_units_year_over_year_trend", 
                            "unique_visitors_trend", 
                            "unique_visitors_year_over_year_trend", 
                            "conversion_rate_trend", 
                            "conversion_rate_year_over_year_trend", 
                            "shipped_cost_of_goods_sold_trend", 
                            "shipped_cost_of_goods_sold_year_over_year_trend", 
                            "page_views_year_over_year_trend",  
                            "page_views_trend",
                            "conversion_percentile", 
                            "x1_week_forecast", 
                            "x4_week_forecast", 
                            "x12_week_forecast", 
                            "shipped_cost_of_goods_sold", 
                            "currency_code")]
                          

#"amazon_ordered_sales_rank", "amazon_shipped_units_rank", "amazon_category_shipped_units_rank", "amazon_subcategory_shipped_units_rank")] -- use later

```

Get all the numerical variables in the dataset
```{r}
num_var = which(sapply(sun, is.numeric)) #index vector numeric variables
num_var= names(num_var) #saving names vector for use later on
num_var
```

Finding correlated variables with the transformed order units
```{r}
library(psych)
library(caret)
library(GGally)
library(Hmisc)

ggcorr(sun[,num_var])
cor(as.matrix(sun[,num_var]))
  
#remove the following correlated
set.seed(222)

#The correlated variables with correlation coefficient above 0.7 is removed 
#The below code has been iterated several times to find the best possible set of fields that can be used in the model
train = sun[, !names(sun) %in% c("shipped_units", "shipped_amount", "unique_visitors_index", "page_views_index", "ordered_amount", "orders", "unfilled_customer_ordered_units", "transformed_order_units", "average_customer_review")] 

num_var = which(sapply(train, is.numeric)) #index vector numeric variables
num_var= names(num_var) #saving names vector for use later on
ggcorr(train[,num_var])
cor(as.matrix(train[,num_var]))
cortest.bartlett(train[,num_var], n=nrow(train))

```

Model 1: Linear Model using the dummy train
1. Create dummy variable for use in model
2. Apply k-fold cross validation
3. The model will be reitrated to remove variables that are not significant to get the best model
4. Anova gives a better perspective of significance for the categorical variables 
List of variables removed -  title, week date start and end, first 2 columns, release date, platform1/2, upc code, asin, category, replenishent category, amazon_subcategory_ordered_units_rank  -list_price  -amazon_category_ordered_units_rank -  -unsellable_on_hand_cost  - amazon_subcategory_shipped_units_rank - unsellable_on_hand_cost     
Results: 86% variation is explained using 22 variables
```{r}
names(train)
dummy_model_lm = dummyVars( ~ ., train[,-c(1:9, 11:12, 36:38)])
dummy_train_lm = data.frame(predict(dummy_model_lm, train[,-c(1:9,11:12, 36:38)]))

# Custom Control Parameters
custom = trainControl(method = "repeatedcv",
                       number = 5,
                       repeats = 2,
                       verboseIter = T)

lm = train(ordered_units ~.  -unsellable_on_hand_cost  -sellable_on_hand_cost -amazon_subcategory_shipped_units_rank -amazon_subcategory_ordered_units_rank  -average_shipped_price -amazon_category_shipped_units_rank 
        -amazon_shipped_sales_rank -amazon_ordered_units_rank -unsellable_on_hand_units  -amazon_shipped_units_rank  - amazon_subcategory_shipped_sales_rank -amazon_category_shipped_sales_rank  -list_price    ,

           #-amazon_subcategory_ordered_units_rank  - -amazon_category_ordered_units_rank -  amazon_subcategory_shipped_units_rank
 #         -amazon_ordered_units_rank - amazon_shipped_sales_rank  -amazon_category_shipped_sales_rank   #-amazon_subcategory_shipped_sales_rank -amazon_shipped_units_rank  -amazon_category_shipped_units_rank                       
           dummy_train_lm,
            method="lm",
            preProcess = c("center", "scale"),
            trControl=custom)
anova(lm$finalModel)

summary(lm)
lm$results
plot(lm$finalModel)
plot(varImp(lm), top=20)
lm$finalModel
dwt(residuals(lm))
```

Model 2: Lasso Model using the dummy train
1. Create dummy variable for use in model
2. Apply k-fold cross validation
3. The model will be reitrated to remove variables that are not significant to get the best model
4. Anova gives a better perspective of significance for the categorical variables 
List of variables removed -  title, week date start and end, first 2 columns, release date, platform1/2, upc code, asin, category, Results: lambda =0.00001 explains 86%
                80% variability is explained by 12-15 variables, hence only 15 top varaibles are chosen

```{r}
names(train)
dummy_model_las = dummyVars( ~ ., train[,-c(1:9, 37:38, 40)])
dummy_train_las= data.frame(predict(dummy_model_las, train[,-c(1:9, 37:38, 40)]))

#capturing J&J req though the variables removed from the model are actually significant. Removing the fields not asked for explains 83% using 12-13 variables

lasso = train(ordered_units ~ . -unsellable_on_hand_cost  -sellable_on_hand_cost   -amazon_subcategory_ordered_units_rank  -average_shipped_price -unsellable_on_hand_units  -amazon_shipped_units_rank  - amazon_subcategory_shipped_sales_rank -amazon_category_shipped_sales_rank -amazon_shipped_units_rank  -amazon_category_shipped_units_rank -amazon_subcategory_shipped_units_rank  - amazon_shipped_sales_rank -amazon_category_shipped_sales_rank  -amazon_subcategory_shipped_sales_rank -amazon_category_ordered_units_rank -amazon_subcategory_ordered_units_rank -amazon_ordered_units_rank,  
               dummy_train_las,
               method="glmnet",
               tuneGrid=expand.grid(alpha=1,
                                    lambda=seq(0.00001, 1, length=20)),
              preProcess = c("center", "scale"),
              trControl=custom)

plot(lasso)
lasso$results

plot(lasso$finalModel, xvar = 'dev', label=T)
plot(varImp(lasso, scale=F), top=13)
dwt(residuals(lasso))

```

Model 3: Elastic net  
1. Create dummy variable for use in model
2. Apply k-fold cross validation
3. The model will be reitrated to remove variables that are not significant to get the best model
4. Anova gives a better perspective of significance for the categorical variables 
List of variables removed -  title, week date start and end, first 2 columns, release date, platform1/2, upc code, asin, category, Results: lambda =0.00001, alpha =1 explains 85%
                80% variability is explained by 21 variables, hence only 20 top varaibles are chosen
```{r}
names(train)
dummy_model_en = dummyVars( ~ ., train[,-c(1:9, 36:38, 40)])
dummy_train_en= data.frame(predict(dummy_model_en, train[,-c(1:9, 36:38, 40)]))

#capturing J&J req though these are actually significant hence removing the fields not asked for explains 83% using 12-13 variables

en = train(ordered_units ~ .  -unsellable_on_hand_cost  -sellable_on_hand_cost -average_shipped_price -unsellable_on_hand_units -amazon_shipped_units_rank  -amazon_category_shipped_sales_rank -amazon_category_shipped_units_rank -amazon_subcategory_shipped_units_rank  - amazon_shipped_sales_rank -amazon_category_shipped_sales_rank  -amazon_subcategory_shipped_sales_rank -amazon_category_ordered_units_rank -amazon_subcategory_ordered_units_rank -amazon_ordered_units_rank -list_price - average_ordered_price ,  
               dummy_train_en ,
               method="glmnet",
               tuneGrid=expand.grid(alpha=seq(0,1,length=10),
                                    lambda=seq(0.00001, 1, length=30)),
               preProcess = c("center", "scale"),
              trControl=custom)

en$results
plot(en$finalModel, xvar = 'dev', label=T)
plot(varImp(en), top=25)
dwt(residuals(en))
```

Model 4: Stepwise selection  
1. Create dummy variable for use in model
2. Apply k-fold cross validation
3. The model will be reitrated to remove variables that are not significant to get the best model
4. Anova gives a better perspective of significance for the categorical variables 
List of variables removed -  title, week date start and end, first 2 columns, release date, platform1/2, upc code, asin,
Results: 25 variables explains 75%
                
```{r}
names(train)
dummy_model_fwd =dummyVars( ~ ., train[,-c(1:9, 11, 12, 36:38, 40)])
dummy_train_fwd= data.frame(predict(dummy_model_fwd, train[,-c(1:9,11, 12,  36:38, 40)]))

#capturing J&J req though these are actually significant hence removing the fields not asked for explains 62% using 11 variables

fwd = train(ordered_units ~ .  -unsellable_on_hand_cost  -sellable_on_hand_cost -average_shipped_price  -amazon_shipped_units_rank  -amazon_category_shipped_sales_rank -amazon_category_shipped_units_rank -amazon_subcategory_shipped_units_rank  - amazon_shipped_sales_rank -amazon_category_shipped_sales_rank  -amazon_subcategory_shipped_sales_rank -amazon_category_ordered_units_rank -amazon_subcategory_ordered_units_rank -amazon_ordered_units_rank - average_ordered_price , 
               
               dummy_train_fwd,
               method="leapForward", 
                   tuneGrid=expand.grid(nvmax=c(2:50)),
            preProcess = c("center", "scale"),
              trControl=custom)

plot(fwd)

plot(varImp(fwd), top=25)
dwt(residuals(fwd))
```

Compare Models 
 The best model is Elastic net which explains 86% variatiom
```{r}
model_list = list(LinearModel=lm, Lasso=lasso, Elasticnet=en, ForwardSelection=fwd)
res = resamples(model_list)
summary(res)
```
Durbin watson
```{r}
library(car)
dw_list = list(LinearModel=dwt(residuals(lm)), 
               Lasso=dwt(residuals(lasso)), 
               Elasticnet=dwt(residuals(en)), 
               ForwardSelection=dwt(residuals(fwd)))
dw_list
```


Final Model using the best model
   alpha    lambda
      1    0.00001
The model as before will use 98 variables (including categorical dummy variables) to explain the 87.66% variability
The list of important variables
product group
category
subcategory
list price
average ordered price
amazon_ordered_sales_rank                     
amazon_category_ordered_sales_rank            
amazon_subcategory_ordered_sales_rank         
customer_reviews                             
page_views_rank                              
open_purchase_order_quantity                  
sellable_on_hand_units                        
replenishment_category
week_number

```{r}
library(glmnet)
en$bestTune

# Save Final Model for Later Use
saveRDS(en, "final_model_en.rds")
fm = readRDS("final_model_en.rds")

final_x= train[,-c(1:9, 36:38, 40)]
final_x= final_x[,(!names(final_x)%in% c("unsellable_on_hand_cost", "sellable_on_hand_cost", "average_shipped_price", "unsellable_on_hand_units", "amazon_shipped_units_rank", "amazon_category_shipped_sales_rank", "amazon_category_shipped_units_rank", "amazon_subcategory_shipped_units_rank",  "amazon_shipped_sales_rank", "amazon_category_shipped_sales_rank", "amazon_subcategory_shipped_sales_rank", "amazon_category_ordered_units_rank", "amazon_subcategory_ordered_units_rank", "amazon_ordered_units_rank", "list_price" , "average_ordered_price"))]

dummy_final= model.matrix( ~ ., final_x)
final=glmnet(x=dummy_final, y=train$ordered_units, family = "gaussian", lambda = en$bestTune[2], alpha = en$bestTune[1])

plot(residuals(lasso))
plot(predict(lasso), residuals(lasso)) #no constant variance
qqplot(predict(lasso),residuals(lasso))
hist(residuals(lasso),main='Histogram of residuals',xlab='Standardised
Residuals',ylab='Frequency')


final$beta
plot(varImp(lasso), top=15)


```
#IF lASSO IS THE BEST 

```{r}
library(glmnet)
lasso$bestTune

# Save Final Model for Later Use
saveRDS(lasso, "final_model_lass.rds")
fm = readRDS("final_model_lass.rds")

final_x= train[,-c(1:9, 36:38, 40)]
final_x= final_x[,(!names(final_x)%in% c("unsellable_on_hand_cost", "sellable_on_hand_cost", "average_shipped_price", "unsellable_on_hand_units", "amazon_shipped_units_rank", "amazon_category_shipped_sales_rank", "amazon_category_shipped_units_rank", "amazon_subcategory_shipped_units_rank",  "amazon_shipped_sales_rank", "amazon_category_shipped_sales_rank", "amazon_subcategory_shipped_sales_rank", "amazon_category_ordered_units_rank", "amazon_subcategory_ordered_units_rank", "amazon_ordered_units_rank", "list_price" , "average_ordered_price"))]

dummy_final= model.matrix( ~ ., final_x)
final=glmnet(x=dummy_final, y=train$ordered_units, family = "gaussian", lambda = lasso$bestTune[2], alpha = lasso$bestTune[1])

plot(residuals(lasso))
plot(predict(lasso), residuals(lasso)) #no constant variance
qqplot(predict(lasso),residuals(lasso))
hist(residuals(lasso),main='Histogram of residuals',xlab='Standardised
Residuals',ylab='Frequency')


final$beta
plot(varImp(lasso), top=20)


```

```{r}
ggplot(sun, aes(x=sort(week_number), y=ordered_units, col=category)) + geom_boxplot() +
  ylim(c(0,4000))

ggplot(sun, aes(x=sort(week_number), y=ordered_units, col=subcategory)) + geom_boxplot() +
  ylim(c(0,4000))   #2 products under 8030 face is popular between 30 and 34th week, why?

tit_subcat=unique(sun[,c("title", "subcategory", "category")])
table(tit_subcat$category, tit_subcat$subcategory) 

table(tit_subcat$title, tit_subcat$subcategory) 

tit_subcat$title[tit_subcat$subcategory == "8030 Face"]
tit_subcat$title[tit_subcat$category == "0900 GM/HBC"]

unique(sun$title[(as.numeric(sun$week_number) >="12" & as.numeric(sun$week_number) >="16") & sun$subcategory == "8090 Sun"])

ggplot(sun, aes(x=as.factor(platform_type), fill=category)) + geom_bar() +
  ylim(c(0,1000)) +  #2 products under 8030 face is popular between 30 and 34th week, why?
  xlab("Platforms") 

ggplot(sun, aes(x=as.factor(platform_type), fill=subcategory)) + geom_bar() +
  ylim(c(0,1000)) +  #2 products under 8030 face is popular between 30 and 34th week, why?
  xlab("Platforms") 

```


Part II

```{r}
factcols = c("amazon_category_ordered_sales_rank", "amazon_subcategory_ordered_sales_rank", "amazon_ordered_units_rank", "amazon_category_ordered_units_rank", "amazon_subcategory_ordered_units_rank", "amazon_shipped_sales_rank", "amazon_category_shipped_sales_rank", "amazon_subcategory_shipped_sales_rank", "amazon_subcategory_shipped_units_rank", "page_views_rank", "page_views_index", "unique_visitors_index")

sun[factcols] = lapply(sun[factcols], factor)
sapply(sun, function(x) sum(is.na(x)))

```


#preserve ordered units and remove unfilled customer ordered units and sellable on hand cost
```{r}
num_var1 = which(sapply(train, is.numeric)) #index vector numeric variables
num_var1= names(num_var1) #saving names vector for use later on
 
features=num_var1[-c(3, 7:16, 20, 22)]
sun_new=train
#scale all the numerical features
sun_new[,features]=scale(sun_new[,features])

sunPCA = prcomp(sun_new[,features], scale = TRUE)
plot(sunPCA, type="l") #variance at second component
summary(sunPCA)
sunPCA$rotation

vars_transformed = apply(sunPCA$x, 2, var)
vars_transformed
vars_transformed/sum(vars_transformed)  #PC1 explains 42% variation and PC2 explains 17% together explaining 59% PC3 explains 10% adding 69%

# First three principal components explains a lot
comp = data.frame(sunPCA$x[,1:3])
# Plot
plot(comp, pch=16, col=rgb(0,0,0.5))

sunpredictPCA = predict(sunPCA, sun_new[,features])
sunPCAcols <- cbind(sun_new, as.data.frame(sunpredictPCA)[,1:3])


ggplot(sunPCAcols, aes(x=PC1, y=PC2)) + 
    geom_point(aes(fill=upc_code),
               colour='black',
               pch=21,
               size=2) +
    theme_bw()

```

```{r}
ggplot(sunPCAcols, aes(x=PC1, y=PC2)) + 
    geom_point(aes(fill=average_customer_reviews_int),
               colour='black',
               pch=21,
               size=2) +
    theme_bw()
```


```{r}
set.seed(145)
library(factoextra)

fviz_nbclust(sunPCAcols[,c('PC1', 'PC2', 'PC3')], kmeans, method = "wss")  #2clusters 0r 5
fviz_nbclust(sunPCAcols[,c('PC1', 'PC2', 'PC3')], kmeans, method = "silhouette") #the second method points to 5
```

```{r}
kClusters = 4
kmeansPCA = kmeans(sunPCAcols[,c('PC1', 'PC2', 'PC3')], kClusters, nstart=25, iter.max = 1000)
ggplot(sunPCAcols, aes(x=PC1, y=PC2)) + 
    geom_point(aes(fill=factor(kmeansPCA$cluster)),
               colour='black',
               pch=21,
               size=2) +
    scale_fill_manual(values = c("black","red", 'green', 'blue', "purple", "orange","white")) +
    guides(fill=guide_legend(title="Cluster")) +
    theme_bw()
kmeansPCA$tot.withinss
library(cluster)
library(plotly)
clusplot(sun_new[,features], kmeansPCA$cluster, color=T, shade=F,labels=0,lines=0, main='k-Means Cluster Analysis')
kmeansPCA$size

```


```{r}
#library(dplyr)
library(reshape2)
sort(table(kmeansPCA$clust))
sunclust = names(sort(table(kmeansPCA$clust)))
#sunCluster = sun_new %>% select(asin:title, product_group:subcategory, list_price:orders, unfilled_customer_ordered_units: sellable_on_hand_units)
sunCluster = sun_new[,c(features, "title", "category", "subcategory", "upc_code", "asin", "platform_type", "replenishment_category", "week_number")]
#sunCluster = sun_new[,!names(sun_new) %in% c("ordered_units", "log_order_units", "week_start", "week_end", "release_date")] 

cluster1=sunCluster[kmeansPCA$clust==sunclust[1],]
c1_uniq=as.data.frame(as.character(unique(cluster1$title)))
names(c1_uniq) = "cluster1"
c1_uniq_week=as.character(sort(unique(cluster1$week_number)))

ggplot(data= melt(cluster1), aes(x=variable, y=value)) +
    stat_boxplot(geom ='errorbar') +
    geom_boxplot(aes(fill=variable)) +
    coord_cartesian(ylim = c(0, 10)) +
    theme(axis.text.x = element_text(angle = 90, hjust = 1), legend.position="none") 

cluster2=sunCluster[kmeansPCA$clust==sunclust[2],]
c2_uniq=as.data.frame(as.character(unique(cluster2$title)))
names(c2_uniq) = "cluster2"
c2_uniq_week=as.character(sort(unique(cluster2$week_number)))

ggplot(data= melt(cluster2), aes(x=variable, y=value)) +
    stat_boxplot(geom ='errorbar') +
    geom_boxplot(aes(fill=variable)) +
   coord_cartesian(ylim = c(0, 10)) +
    theme(axis.text.x = element_text(angle = 90, hjust = 1), legend.position="none") 

cluster3=sunCluster[kmeansPCA$clust==sunclust[3],]
c3_uniq=as.data.frame(as.character(unique(cluster3$title)))
names(c3_uniq) = "cluster3"
c3_uniq_week=as.character(sort(unique(cluster3$week_number)))

ggplot(data= melt(cluster3), aes(x=variable, y=value)) +
    stat_boxplot(geom ='errorbar') +
    geom_boxplot(aes(fill=variable)) +
    coord_cartesian(ylim = c(0, 10)) +
    theme(axis.text.x = element_text(angle = 90, hjust = 1), legend.position="none") 

cluster4=sunCluster[kmeansPCA$clust==sunclust[4],]
c4_uniq=as.data.frame(as.character(unique(cluster4$title)))
names(c4_uniq) = "cluster4"
c4_uniq_week=as.character(sort(unique(cluster4$week_number)))

ggplot(data= melt(cluster4), aes(x=variable, y=value)) +
    stat_boxplot(geom ='errorbar') +
    geom_boxplot(aes(fill=variable)) +
    coord_cartesian(ylim = c(0, 5)) +
    theme(axis.text.x = element_text(angle = 90, hjust = 1), legend.position="none") 

cluster5=sunCluster[kmeansPCA$clust==sunclust[5],]
c5_uniq=as.data.frame(as.character(unique(cluster5$title)))
names(c5_uniq) = "cluster5"
c5_uniq_week=as.character(sort(unique(cluster5$week_number)))

ggplot(data= melt(cluster5), aes(x=variable, y=value)) +
    stat_boxplot(geom ='errorbar') +
    geom_boxplot(aes(fill=variable)) +
    coord_cartesian(ylim = c(0,5)) +
    theme(axis.text.x = element_text(angle = 90, hjust = 1), legend.position="none") 

cluster6=sunCluster[kmeansPCA$clust==sunclust[6],]
c6_uniq=as.data.frame(as.character(unique(cluster6$title)))
names(c6_uniq) = "cluster6"
c6_uniq_week=as.character(sort(unique(cluster6$week_number)))

ggplot(data= melt(cluster5), aes(x=variable, y=value)) +
    stat_boxplot(geom ='errorbar') +
    geom_boxplot(aes(fill=variable)) +
    coord_cartesian(ylim = c(0, 7.5)) +
    theme(axis.text.x = element_text(angle = 90, hjust = 1), legend.position="none") 


library(qpcR)
product_clusters=qpcR:::cbind.na(c1_uniq, c2_uniq, c3_uniq, c4_uniq)
product_clusters

#p <- plot_ly(carsDf,x=Comp.1,y=Comp.2,text=rownames(carsDf),
#             mode="markers",color = cluster_name,marker=list(size=11))
#p <- layout(p,title="PCA Clusters from Hierachical Clustering of Cars Data",
#            xaxis=list(title="PC1"),
#            yaxis=list(title="PC2"))
(product_clusters$cluster1)
length(product_clusters$cluster2)
length(product_clusters$cluster3)
length(product_clusters$cluster4)
length(product_clusters$cluster5)
length(product_clusters$cluster6)

```

```{r}
c1=unique(cluster1$title)
c2=unique(cluster2$title)
c3=unique(cluster3$title)
c1_not_in_c2 = unique(cluster1$title[!cluster1$title %in% c2])
c1_not_in_c3 = unique(cluster1$title[!cluster1$title %in% c3])

c2_not_in_c1 = unique(cluster2$title[!cluster2$title %in% c1])
common = unique(cluster2$title[cluster2$title %in% c1])

(c1_not_in_c2)
(c2_not_in_c1)
(c1_not_in_c3)

(common)
```

CLUSTERING WITHOUT PCA
```{r}
set.seed(145)
fviz_nbclust(sun_new[,num_var1], kmeans, method = "wss")  #2clusters 0r 5
fviz_nbclust(sun_new[,num_var1], kmeans, method = "silhouette") 
wss = sum(kmeans(sun_new[,c('log_order_units')], centers=1)$withinss) #find variance in PC1 and PC2

for (i in 2:15) wss[i] = sum(kmeans(sun_new[,c('log_order_units')],
                                     centers=i)$withinss)

plot(1:15, wss, type="b", xlab="Number of Clusters",
     ylab="Within groups sum of squares")

```
```{r}
kClusters = 3
kmeans_orig = kmeans(sun_new[,num_var1], kClusters)
ggplot(sun_new, aes(x=average_customer_reviews_int, y=ordered_units)) + 
    geom_point(aes(fill=factor(kmeans_orig$cluster)),
               colour='black',
               pch=21,
               size=2) +
    scale_fill_manual(values = c("black","red", 'green', 'blue', "purple", "orange")) +
    guides(fill=guide_legend(title="Cluster")) +
    theme_bw()
```

```{r}
library(dplyr)
library(reshape2)
sort(table(kmeans_orig$clust))
clust = names(sort(table(kmeans_orig$clust)))
Cluster = sun_new[,!names(sun_new) %in% c("ordered_units", "log_order_units", "week_start", "week_end", "release_date")] 

cluster1=Cluster[kmeans_orig$clust==clust[1],]
c1_uniq=as.data.frame(as.character(unique(cluster1$title)))
names(c1_uniq) = "cluster1"
c1_uniq_week=as.character(sort(unique(cluster1$week_number)))

ggplot(data= melt(cluster1), aes(x=variable, y=value)) +
    stat_boxplot(geom ='errorbar') +
    geom_boxplot(aes(fill=variable)) +
    coord_cartesian(ylim = c(0, 12)) +
    theme(axis.text.x = element_text(angle = 90, hjust = 1), legend.position="none") 

cluster2=Cluster[kmeans_orig$clust==clust[2],]
c2_uniq=as.data.frame(as.character(unique(cluster2$title)))
names(c2_uniq) = "cluster2"
c2_uniq_week=as.character(sort(unique(cluster2$week_number)))

ggplot(data= melt(cluster2), aes(x=variable, y=value)) +
    stat_boxplot(geom ='errorbar') +
    geom_boxplot(aes(fill=variable)) +
    coord_cartesian(ylim = c(0, 12)) +
    theme(axis.text.x = element_text(angle = 90, hjust = 1), legend.position="none") 

cluster3=Cluster[kmeans_orig$clust==clust[3],]
c3_uniq=as.data.frame(as.character(unique(cluster3$title)))
names(c3_uniq) = "cluster3"
c3_uniq_week=as.character(sort(unique(cluster3$week_number)))

ggplot(data= melt(cluster3), aes(x=variable, y=value)) +
    stat_boxplot(geom ='errorbar') +
    geom_boxplot(aes(fill=variable)) +
    coord_cartesian(ylim = c(0, 12)) +
    theme(axis.text.x = element_text(angle = 90, hjust = 1), legend.position="none") 

cluster4=Cluster[kmeans_orig$clust==clust[4],]
c4_uniq=as.data.frame(as.character(unique(cluster4$title)))
names(c4_uniq) = "cluster4"
c4_uniq_week=as.character(sort(unique(cluster4$week_number)))

ggplot(data= melt(cluster4), aes(x=variable, y=value)) +
    stat_boxplot(geom ='errorbar') +
    geom_boxplot(aes(fill=variable)) +
    coord_cartesian(ylim = c(0, 12)) +
    theme(axis.text.x = element_text(angle = 90, hjust = 1), legend.position="none") 

cluster5=Cluster[kmeans_orig$clust==clust[5],]
c5_uniq=as.data.frame(as.character(unique(cluster5$title)))
names(c5_uniq) = "cluster5"
c5_uniq_week=as.character(sort(unique(cluster5$week_number)))

ggplot(data= melt(cluster5), aes(x=variable, y=value)) +
    stat_boxplot(geom ='errorbar') +
    geom_boxplot(aes(fill=variable)) +
    coord_cartesian(ylim = c(0, 7.5)) +
    theme(axis.text.x = element_text(angle = 90, hjust = 1), legend.position="none") 

par(mfrow=c(2,2))


library(qpcR)
product_clust_kmean=qpcR:::cbind.na(c1_uniq, c2_uniq, c3_uniq) # c4_uniq, c5_uniq)
product_clust_kmean

library(cluster)
clusplot(sun_new[,num_var1], kmeans_orig$cluster, color=T, shade=F,labels=0,lines=0, main='k-Means Cluster Analysis')

#table(product_clust_kmean)
#nrow(product_clust_kmean$cluster2)
```
Binning
```{r}
breaks = c(0,500,1000,1500,2000, 4000)
sun_new$category_ordered_rank = findInterval(sun_orig$amazon_category_ordered_units_rank, breaks)
hist(sun_new$category_ordered_rank)

breaks = seq(1,350,70)
sun_new$subcategory_ordered_rank = findInterval(sun_new$amazon_subcategory_ordered_units_rank, breaks)
hist(sun_new$subcategory_ordered_rank)

breaks=seq(1,  35500000, 7100000)
sun_new$page_view_rank_bin = findInterval(sun_new$page_views_rank, breaks)
hist(sun_new$page_view_rank_bin)

breaks=seq(1,  20, 5)
sun_new$unique_visitor_index_bin = findInterval(sun_new$unique_visitors_index, breaks)
hist(sun_new$unique_visitor_index_bin)

breaks=seq(1,  2200000, 420000)
sun_new$order_units_bin = findInterval(sun_new$amazon_ordered_units_rank, breaks)
hist(sun_new$order_units_bin)
```
