---
title: "JJ forecasting"
author: "Annie George"
date: "November 19, 2018"
output: slidy_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## R Markdown

This is an R Markdown presentation. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.

## Slide with Bullets

- Bullet 1
- Bullet 2
- Bullet 3

## Slide with R Output

```{r}
library(readxl)
library(xlsx)
library(sqldf)
library(dplyr)
library(tidyr)
library(janitor)
library(fpp2)

```

```{r cars, echo = TRUE}
sun=read_excel("sun_drivers.xlsx",  col_names=TRUE)
sun=clean_names(sun)
fc=sun%>% group_by(week_start) %>%summarise(Order_units=sum(ordered_units))
fc=na.omit(fc) 

fc$week_start=as.Date(fc$week_start)
sun_ts <- ts(fc$Order_units)
tsclean(sun_ts)

library(xts)
library(lubridate)
sun_ts <- ts(fc$Order_units, freq=52, start=c(2014,25), end=c(2017,21)) 

sun_ts <- ts(fc$Order_units, 
   freq=365.25/7, 
     start= decimal_date(ymd("2014-06-15")))
sun_ts=as.xts(sun_ts)
autoplot(sun_ts) +
  ggtitle("Order units sold for Neutrogena brand - Weekly data") +
  xlab("Year") +
  ylab("Order Units")

sun_ts_train =  window(sun_ts, start , 
     start= decimal_date(ymd("2014-06-15")))


ggseasonplot(sun_ts, year.labels=TRUE, year.labels.left=TRUE) +
  ylab("$ million") +
  ggtitle("Seasonal plot: Order units")

ggseasonplot(sun_ts, polar=TRUE) +
  ylab("$ million") +
  ggtitle("Polar seasonal plot: Order units sold")
ggsubseriesplot(sun_ts) +
  ylab("$ million") +
  ggtitle("Seasonal subseries plot: Order units sold")


sun1 <- window(sun_ts, start=c(2014,06)sun, end=c(2017,04))
gglagplot(sun1)
ggAcf(sun1, lag=52)

autoplot(sun1) +
  autolayer(meanf(sun1, h=11),
            series="Mean", PI=FALSE) +
  autolayer(naive(sun1, h=11),
            series="Naïve", PI=FALSE) +
  autolayer(snaive(sun1, h=11),
            series="Seasonal naïve", PI=FALSE) +
  autolayer(rwf(sun1, drift=TRUE, h=40),
            series="Drift", PI=FALSE) +
  ggtitle("Forecasts for weekly order units sales") +
  xlab("Year") + ylab("Order Units sales") +
  guides(colour=guide_legend(title="Forecast"))


checkresiduals(naive(sun1))  #not stationary

sunfit1 <- meanf(sun1,h=3)
sunfit2 <- rwf(sun1,h=3)
autoplot(window(sun_ts, start=c(2014,25))) +
  autolayer(sunfit1, series="Mean", PI=FALSE) +
  autolayer(sunfit2, series="Naïve", PI=FALSE) +
  xlab("Year") + ylab("Order units") +
  ggtitle("Forecasts for order units sales") +
  guides(colour=guide_legend(title="Forecast"))
sun2 <- window(sun_ts, start=c(2017,01))
accuracy(sunfit1, sun2)
accuracy(sunfit2, sun2)
accuracy(beerfit3, beer3)





decompose(sun_ts) %>% autoplot()

```

## Slide with Plot

```{r pressure}
plot(pressure)
```

